---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# jaesan
# WORKING IN PROGRESS

<!-- badges: start -->
<!-- badges: end -->

The goal of jaesan is to provide data about property of people who work or worked for Korea.

## Installation

# NOT YET. PLEASE USE GITHUB

You can install the released version of jaesan from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("jaesan")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("mrchypark/jaesan")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(jaesan)
query("전")
query("노")
query("김")
query("이명")
query("박")
query("김학")
```

recode data from 2011 to 2018 available.

```{r}
library(dplyr)
library(purrr)

2011:2018 %>%
  paste0("recode", .) %>% 
  iwalk(
    ~ glimpse(get(.x))
  )
```
